\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeResearchExp}[2]{
\vspace{0.5mm}\item
        \textbf{#1} 
        {#2}
    % \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#2}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{Abdul Qadir}}\\
    {\textit{Vulnerability Researcher \& Reverse Engineer}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +92-309-554-4409 | \href{mailto:0xabdulqadir@gmail.com}{0xabdulqadir@gmail.com} | 
    \href{https://0xnull007.github.io/}{0xnull007.github.io}
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/0xnull007/}{0xnull007} | 
    \socialicon{\faGithub} \href{https://github.com/0xnull007}{0xnull007} |
    \socialicon{\faTwitter} \href{https://twitter.com/0xnull007}{0xnull007}
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Lahore, Punjab - 53000, Pakistan}
\end{center}
\vspace{-4mm}

\section{\textbf{Professional Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeSubheading
    {Rendream [\href{https://rendream.com/}{\faIcon{globe}}]}{Lahore, Pakistan}
    {Executive Reverse Engineer}{September 2025 -- Current}
    \resumeItemListStart
      \item Automated product execution at Chrome OS boot on the Chromebook, overcoming restrictive platform constraints by architecting a secure, reliable startup integration across device models.
      \item Explored the Bluetooth Low Energy (BLE) communication protocol used by AirPods.  
      \item Leading the exploration of wired iPhone–MacBook communication protocols to enumerate device interfaces and safely extract device information over USB, producing tools and formal reports.
    \resumeItemListEnd

\resumeSubheading
    {Ebryx (Pvt.) Ltd. [\href{https://www.ebryx.com}{\faIcon{globe}}]}{Lahore, Pakistan}
    {Malware Researcher}{Apr 2024 -- Sep 2025}
    \resumeItemListStart
      \item Conducted reverse engineering of malware families (LockBit, BlackBasta, ScarletEel), analyzing persistence mechanisms, cryptographic implementations (ChaCha20, RSA, etc.), and evasion techniques to extract functionality and generate threat intelligence.
      \item Performed pentesting of enterprise products (ZTNA, VPNs, etc.), reviewing authentication, access control, and protocol implementations to identify weaknesses and improve overall system resilience.
      \item Researched and weaponized Linux kernel n-day vulnerabilities, carrying out exploit analysis, proof-of-concept development, and mitigation validation to strengthen OS-level security.
      \item Reversed and analyzed mobile and desktop applications using static and dynamic methods; applied runtime instrumentation (Frida, Magisk) for SSL pinning bypass, encryption validation, and tampering detection.
      \item Utilized program analysis and debugging tools (IDA Pro, Ghidra, Radare2, GDB, WinDbg) to dissect binaries across architectures (x86, x64), identifying code functionality and undocumented behaviors.
      \item Conducted adversary simulations with Havoc and Sliver, developing custom loaders and droppers to test endpoint defenses and evaluate incident response effectiveness.
    \resumeItemListEnd

  \resumeSubheading
    {University of the Punjab [\href{https://www.pu.edu.pk}{\faIcon{globe}}]}{Lahore, Pakistan}
    {Teaching Assistant}{Jan 2023 -- Jul 2024}
    \resumeItemListStart
      \item Designed and delivered lab coursework for OOP, DSA, and Operating Systems courses.
      \item Created and graded lab examinations, ensuring alignment with course objectives.
      \item Assisted students in lab sessions and handled other TA responsibilities.
    \resumeItemListEnd
\resumeSubHeadingListEnd
  
\vspace{-6mm}
\section{\textbf{Research Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeResearchExp
  {Linux Kernel \& Userland Vulnerability Research (n-day Exploits)}{}
{
\resumeItemListStart
  \item Analyzed and reproduced critical Linux kernel vulnerabilities including \textbf{Dirty Pipe (CVE-2022-0847)} and \textbf{Dirty COW (CVE-2016-5195)}, focusing on memory management, page cache, and race conditions enabling privilege escalation.  
  \item Built custom kernel environments in QEMU with GDB (gef) to trace vulnerable code paths, study memory write primitives, and confirm local root escalation through working PoCs.  
  \item Implemented a Proof-of-Concept for \textbf{Sudo pwfeedback (CVE-2019-18634)}, demonstrating a stack-based buffer overflow and analyzing exploitability for local privilege escalation.  
  \item Utilized Elixir Bootlin, source-level debugging, and controlled race condition exploitation to understand vulnerability root causes and validate mitigations.  
\resumeItemListEnd
}


\resumeResearchExp
  {Vulnerability Research \& Exploit Development for Linux Kernel [\href{https://github.com/0xnull007/linux_kernel_exploitation/}{\faIcon{globe}}] }
{
\resumeItemListStart
  \item Final Year Project (FYP) during Bachelor
  \item Supervised by Dr. Muhammad Arif Butt \href{https://arifbutt.me}{(arifbutt.me)}
  \item Started binary exploitation from Linux user-land and extended into kernel-land exploitation
  \item Conducted n-day research on CVE-2022-0185 (Linux Kernel fscontext buffer overflow vulnerability)
\resumeItemListEnd
}

\resumeProject
  {Linux eBPF-based Modular Firewall
  [\href{https://github.com/0xnull007/EBPF-Firewall}{\faIcon{globe}}] 
  }
  {Tools: C, bash}
  {}
  {}
\resumeItemListStart
  \item Built a high-performance firewall using eBPF with XDP and TC hooks, enabling real-time packet filtering, rate limiting, and protocol/IP/port-based controls.
  \item Implemented dynamic rule management through user-space utilities with pinned BPF maps for persistence.
\resumeItemListEnd


\vspace{-7mm}
\resumeSubHeadingListEnd

\section{\textbf{Skills}}
\vspace{-0.4mm}
 \resumeHeadingSkillStart
  \resumeItem{Programming: }
    {C/C++, Assembly (x86-64/ARM), Bash, Python, Java, JavaScript}
  \resumeItem{Information Security: }
    {Vulnerability Research \& Exploit Development, Incident Detection \& Response, Secure Development Practices}
  \resumeItem{Networks: }
    {Firewalls, Routers, Switches, TCP/IP, VPNs, Network Security Architecture, Network Traffic Analysis (Wireshark, nftables)}
  \resumeItem{Cryptography: }
    {Symmetric \& Asymmetric Encryption (ChaCha20, AES, RSA), Hashing Algorithms (SHA, MD5), Key Management, Secure Protocols \& Communication Analysis}
  \resumeItem{Tools: }
    {QEMU/KVM, VMWare Workstation, IDA Pro, Ghidra, Radare2, GDB with GEF, AFL++, Syzkaller, CodeQL, Frida, Objection, Wireshark, Kali Toolchain, FlareVM Toolchain}
  \resumeItem{Operating Systems: }
    {Linux Kernel (Ubuntu, Debian), Windows (WSL), Android}
  \resumeItem{Research \& CTF Skills: }
    {Binary Exploitation, Reverse Engineering, Kernel Exploitation, Web Exploitation, Memory Corruption Analysis, Challenge Development}
 \resumeHeadingSkillEnd

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{PUCIT, University of the Punjab}{Lahore, Pakistan}
{Bachelor of Computer Science}{Dec 2020 - July 2024}
\resumeItemListStart
\item GPA: 3.05/4.00
\item Cyber-security lead at Google Developer Student Clubs at PUCIT
\item Mentor and CTF challenge author at PUCon24 \& PUCon25 (National Tech Event by University of the Punjab) [\href{https://pucon.vercel.app/}{\faIcon{globe}}]
\item Lead at Cyber@PU - Unofficial PUCIT Cyber Security Community
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{University Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {Hotel Management System}
  {Tools: JavaScript, Node.js, MySQL}
  {}
  {{}[\href{https://github.com/0xnull007/Hotel-managemant-System}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Developed a full-stack web application with an admin panel for hotel services including room booking and employee management.
  \item Led the project team, implementing backend logic in Node.js with MySQL for data persistence.
\resumeItemListEnd

\resumeProject
  {Web Engineering Course Material}
  {Tools: Java, Servlets, JSP, MySQL, Batch Scripts}
  {{}[\href{https://github.com/0xnull007/demo}{\textcolor{darkblue}{\faGithub}}]}
  {{}[\href{https://github.com/0xnull007/Web-Engineering}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Solved labs covering client-side and server-side programming, session handling, authentication, and database connectivity using Java Servlets and JSP.
  \item Automated the entire build and execution process using batch scripts to replace IDE usage and streamline development.
\resumeItemListEnd

\resumeProject
  {Network Programming in Linux}
  {Tools: C, Linux Sockets, TCP/IP}
  {}
  {{}[\href{https://github.com/0xnull007/network_programming}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Implemented socket programming concepts in C, including TCP/UDP communication, client-server architecture, and concurrent connections in Linux.
  \item Explored low-level system calls to deepen understanding of network protocols and inter-process communication.
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}